Packaging research artifacts with RO-Crate

### 2021-05-03 latex/ro-crate.tex
markdown settings

% add. options: [seceqn,secthm,crcready]
\documentclass[ds]{iosart2x}
\usepackage[utf8]{inputenc}
\usepackage[smartEllipses]{markdown}
\def\markdownOptionOutputDir{../output}

@@

\pubyear{0000}
\volume{0}
\firstpage{1}
\lastpage{1}

@@

% Two or more authors:
\author[A,B]{\inits{S.S-R.}\fnms{Stian} \snm{Soiland-Reyes}\ead[label=e1]{soiland-reyes@manchester.ac.uk}\ead[label=o1,orcid]{0000-0001-9842-9718}%
\thanks{Corresponding author. \printead{e1}.}},
\author[C]{\inits{P.S.}\fnms{Peter} \snm{Sefton}\ead[label=e2]{Peter.Sefton@uts.edu.au}\ead[label=o2,orcid]{0000-0002-3545-944X}},
\author[A]{\inits{C.G.}\fnms{Carole} \snm{Goble}\ead[label=e3]{carole.goble@manchester.ac.uk}\ead[label=o3,orcid]{0000-0003-1219-2137}},
\author[B]{\inits{P.G.}\fnms{Paul} \snm{Groth}\ead[label=e3]{p.t.groth@uva.nl}\ead[label=o3,orcid]{0000-0003-0183-6910}}
\address[A]{Computer Science, \orgname{The University of Manchester},
\cny{UK}\printead[presep={\\}]{e1,o1}}
\address[B]{Informatics Institute, \orgname{University of Amsterdam},
\cny{The Netherlands}\printead[presep={\\}]{e2,o2}}
\address[C]{Faculty of Science, \orgname{University Technology Sydney},
\cny{Australia}\printead[presep={\\}]{e3,o3}}

>>>>

% add. options: [seceqn,secthm,crcready]
\documentclass[ds]{iosart2x}
\usepackage[utf8]{inputenc}
\usepackage[smartEllipses,tableCaptions,pipeTAbles,fencedCode,footnotes,underscores]{markdown}
\def\markdownOptionOutputDir{../output}

@@

\pubyear{2021}
\volume{0}
\firstpage{1}
\lastpage{1}

@@

% Two or more authors:
\author[A,B]{\fnms{Stian} \snm{Soiland-Reyes}\ead[label=e1]{soiland-reyes@manchester.ac.uk}\ead[label=o1,orcid]{0000-0001-9842-9718}%
\thanks{Corresponding author. \printead{e1}.}},
\author[C]{\inits{P.S.}\fnms{Peter} \snm{Sefton}\ead[label=e2]{Peter.Sefton@uts.edu.au}\ead[label=o2,orcid]{0000-0002-3545-944X}},
\author[A]{\inits{C.G.}\fnms{Carole} \snm{Goble}\ead[label=e3]{carole.goble@manchester.ac.uk}\ead[label=o3,orcid]{0000-0003-1219-2137}},
\author[B]{\inits{P.G.}\fnms{Paul} \snm{Groth}\ead[label=e3]{p.t.groth@uva.nl}\ead[label=o3,orcid]{0000-0003-0183-6910}}
\address[A]{Computer Science, \orgname{The University of Manchester},
\cny{UK}\printead[presep={\\}]{e1,o1}}
\address[B]{Informatics Institute, \orgname{University of Amsterdam},
\cny{The Netherlands}\printead[presep={\\}]{e2,o2}}
\address[C]{Faculty of Science, \orgname{University Technology Sydney},
\cny{Australia}\printead[presep={\\}]{e3,o3}}
